---
title: "Assessment of the correlation between BMI and the process of Intubation in female patients"
author: "Marina N.E. Hillen"
date: "`r date()`"
format:
  html:
    toc: true
    code-fold: show
    code-tools: true
  pdf:
    toc: true
  docx:
    toc: true
embed-resources: true
editor: visual
---

```{r}
#| output: false #zeigt Consolen-Output 
#| echo: false  #Code will not be echoed (not shown)
#| warning: false

# to add code snipplets: press the green Cplus button top right
# the code snipplets need to start and end with 3 back-ticks, link to R by indicating{r}```

# load libraries
library(here)
library(tidyverse)
library(lubridate)
library(ggplot2)
library(unibeCols)
```

## Introduction
The aim of short analysis is to visualize the correlation between BMI and the process of Intubation in female patients over 30 years of age. 

## Data
We read and process the data as reported by [ Amy S. Nowacki, ’Laryngoscope Dataset’, TSHS Resources Portal (2017)](https://www.causeweb.org/tshs/laryngoscope/).


```{r}
#| output: false
#| echo: false
#| warning: false

# load data
library(medicaldata)
data(laryngoscope)

# Process data
laryngoscope <- laryngoscope |>
  filter(gender == 0) |>
  filter(age > 30)
```

```{r}
#| echo: false
#| warning: false
#| label: fig-laryngoscope
#| fig-cap: "correlation between BMI and total Intubation time"
#| fig-width: 4
#| fig-height: 4

ggplot(laryngoscope, aes(x = BMI, y = total_intubation_time)) +
  geom_point(alpha = 0.5, size = 3) +  # Add scatter points
  geom_smooth(method = "lm", se = FALSE) +  # Add linear regression line
  labs(x = "BMI", y = "Total Intubation Time") +
  theme_minimal() +
  theme(axis.title = element_text(size = 14),  # Increase axis title size
        axis.text = element_text(size = 12))  # Increase axis text size

```
## Conclusions

@fig-laryngoscope does not show the clear correlation between BMI and time until successfull intubation, that was expected from the authors experience in the veterinary field.