---
title: "report on the second wave of COVID-19 in Switzerland"
author: "Marina N. E. Hillen"
date: "`r date()`"
format:
  html:
    toc: true
    code-fold: show
    code-tools: true
  pdf:
    toc: true
  docx:
    toc: true
editor: visual
---

```{r}
#| output: false #zeigt Consolen-Output 
#| echo: false  #Code will not be echoed (not shown)
#| warning: false

# to add code snipplets: press the green Cplus button top right
# the code snipplets need to start and end with 3 back-ticks and link to R by indicating ```{r}```

# load libraries
library(here)
library(tidyverse)
library(lubridate)
library(ggplot2)
library(unibeCols)
```

## Introduction

The aim of this excercise is to visualize the increase in laboratory-confirmed cases of COVID-19 in Switzerland during autumn 2020.

## Data

We read and process the data as reported by the [Federal Office of Public Health](https://idd.bag.admin.ch/).

```{r}
#| output: false
#| echo: false
#| warning: false
cases <- read_csv(here("data/raw/COVID19Cases_geoRegion.csv"))
```

```{r}
#| output: false
#| echo: false
#| warning: false
# Process data
region <- "CH"
window_start <- ymd("2020-09-01")
window_end <- ymd("2020-11-30")
cases <- cases |>
  filter(geoRegion == region & datum >= window_start & datum <= window_end) |>
  select(datum, entries)
cases
```

The figure shows the number of laboratory-confirmed cases of COVID in Switzerland from `r window_start` to `r window_end`.

```{r}
#| echo: false
#| label: fig-cases
#| fig-cap: "laboratory-confirmed cases of COVID in Switzerland in 2020"
#| fig-width: 8
#| fig-height: 4

ggplot(cases, aes(x = datum, y=entries)) +
  geom_bar(stat = "identity", fill = unibeSaphire())+
  labs(x = "", y = "laboratory-confirmed cases of COVID")+
  theme_minimal()
```

## Conclusions

@fig-cases shows: The number of laboratory-confirmed cases of COVID in Switzerland increased.
